\MakeAbstract{
    同济大学（英语：Tongji University），简称同济，是位于中国上海市的一所综合性大学，是中华人民共和国教育部直属的全国重点大学，行政级别为副部级，是“双一流A类”和原“985工程”、原“211工程”重点建设大学，同时是卓越大学联盟、全球环境与可持续发展合作联盟(GUPES)、国际设计艺术院校联盟(Cumulus)、21世纪学术联盟(AC21)、同济-伯克利工程联盟(Tongji-Berkeley Alliance)、中俄工科大学联盟(ASRTU)成员。

    同济大学的前身是1907年创办的德文医学堂，后改名为同济德文医学堂；1912年与创办不久的同济德文工学堂合并，更名为同济德文医工学堂；1923年正式定名为同济大学；1927年成立国立同济大学，是中国最早的七所国立大学之一；1949年更名为同济大学。

    同济大学目前共设有38个学院（系）和二级办学机构，7家附属医院，5所附属中学；有全日制本科生1.7万余人，硕士研究生1.3万余人，博士研究生近5000人。有外国留学生数千人；学校占地面积约3850亩；纸本图书400余万册。

    根据2021年的QS世界大学排名和泰晤士高等教育世界大学排名，同济大学分别位列中国第九和第十六。
}{同济大学，上海，综合性大学，重点大学}

\MakeAbstractEng{
    Tongji University (Chinese: 同济大学) is a national public research university located in Shanghai. Established in 1907 by the German government together with German physicians in Shanghai, Tongji is one of the longest-standing, most selective, and most prestigious universities in China under the Project 985 and Double First Class University Plan. It is a Chinese state Class A Double First Class University.

    Tongji University is renowned for its architecture, engineering and business programs which consistently rank among the best in the world. Tongji's architecture program was rated the top overall architecture program in China according to China's University and College Admission System (CACUS) and ranks as the \nth{13} best architecture program in the world according to the QS World University Rankings. The College of Civil Engineering is considered the best in the world according to several widely cited international rankings, including Shanghai Ranking, U.S. News Rankings, URAP ranking and NTU Ranking. The U.S. News \& World Report Best Global University Ranking ranks Tongji University at \nth{15} worldwide in engineering. The School of Design and Innovation was ranked \nth{12} among art and design schools worldwide in 2022, and the top in Asia, according to the QS. The School of Economics and Management (Tongji SEM) is one of 74 business schools in the world being triple accredited by the European Quality Improvement System (EQUIS), the Association to Advance Collegiate Schools of Business (AACSB) and the Association of MBAs (AMBA). Tongji University is a member of the Yangtze Delta Universities Alliance and Asian-European Laotse Universities Network. According to the 2022 QS World University Rankings, Tongji University ranked \nth{8} nationally. Tongji University consistently features in the top \nth{300} global universities.
}{Tongji University, Shanghai, comprehensive university, key university}
